\hypersetup{linkcolor=black}%
%\malzheading{ Refereed publications}%% use \etal when there are >9 authors!

%Conceptualization
%Data curation
%Formal analysis
%Funding acquisition
%Investigation
%Methodology
%Project administration
%Resources
%Software
%Supervision
%Validation
%Visualization
%Writing - original draft.
%Writing - review & editing

\malzheading{Publications}
\hypersetup{linkcolor=grey}
%\deemph{19 completed peer review; 10 as (co-)lead author; H-index=11}

%{\setlength{\baselineskip}{1ex}
{\fontsize{9pt}{5pt}\selectfont\textcolor{grey}{AIM has been awarded Builder Status within the LSST-DESC, which grants authorship rights on all DESC publications enabled by his work on photometric redshifts, time-domain classification, and service to the collaboration; 
however, he has chosen to only co-author papers to which he made \textit{a direct, scientific contribution}.}\par}
%}\par
%\setlength{\baselineskip}{1em}

\begin{list}{\pubnumber{\therefpubnum}}{\malzlist}
%\item ReSSpect metrics
%\item RAIL v1
%\item pzflow paper
%\item ELAsTiCC metrics
%\item ELAsTiCC release note
%\item CASTORpz
%\item recidivator/pollock?
%\item SCIPPR

\item A. Gagliano, G. Contardo, D. Foreman-Mackey, {\bf A.I. Malz}, P.D. Aleo. 2022. {\em submitted to ApJ 3 October 2022.} First Impressions: Early-Time Classification of Supernovae using Host Galaxy Information and Shallow Learning.
\descr{Contributor: data curation, resources, software, writing}% (review/editing)}
  
\item {\bf A.I. Malz}, F. Lanusse, J.F. Crenshaw, M.L. Graham. 2021. {\em to be submitted to ApJS.} \arxiv{2104.08229}{An information-based metric for observing strategy optimization, demonstrated in the context of photometric redshifts with applications to cosmology}
 \descr{{\bf Lead author}: conceptualization, data curation, formal analysis, funding acquisition, investigation, methodology, software, validation, visualization, writing}% (original draft)}% \& review/editing)}
	
\item R. Hlo{\v z}ek, {\bf A.I. Malz}, K.A. Ponder, M. Dai, G. Narayan, E.E.O. Ishida,% et al.
 T. Allam Jr., A. Bahmanyar, R. Biswas, L. Galbany, S.W. Jha, D.O. Jones, R. Kessler, M. Lochner, A.A. Mahabal, K.S. Mandel, J.R. Martinez-Galarza, J.D. McEwen, D. Muthukrishna, H.V. Peiris, C.M. Peters, C.N. Setzer. 2020. {\em submitted to ApJS 22 December 2020.} 
\arxiv{2012.12392}{Results of the Photometric LSST Astronomical Time-series Classification Challenge (PLAsTiCC)}
	\descr{{\bf Lead author}: conceptualization, formal analysis, investigation, methodology, visualization, writing}% (original draft)}% \& review/editing)}

\item  M. Lokken, A. Gagliano, G. Narayan, R. Hlo{\v z}ek, R. Kessler, J.F. Crenshaw, L. Salo, C.S. Alves, D. Chatterjee, M. Vincenzi, {\bf A.I. Malz}. 2023. MNRAS 520 2. \doi{10.1093/mnras/stad302}{The Simulated Catalogue of Optical Transients and Correlated Hosts (SCOTCH)}
\descr{Contributor: conceptualization, data curation, methodology}% (original draft)}% \& review/editing)}

\item N. Stylianou, {\bf A.I. Malz}, P. Hatfield, J.F. Crenshaw, J. Gschwend. 2021. PASP 134 1034. \doi{10.1088/1538-3873/ac59bf}{The sensitivity of GPz estimates of photo-z posterior PDFs to realistically complex training set imperfections}
\descr{{\bf Lead author}: conceptualization, data curation, formal analysis, funding acquisition, investigation, methodology, software, supervision, validation, visualization, writing}% (original draft)}% \& review/editing)}

\item {\bf A.I. Malz}, D.W. Hogg. 2021. ApJ 928 127. \doi{10.3847/1538-4357/ac062f}{How to obtain the redshift distribution from probabilistic redshift estimates}
	\descr{{\bf Lead author}: conceptualization, data curation, formal analysis, funding acquisition, investigation, methodology, software, validation, visualization, writing}% (original draft)}% \& review/editing)}
	
\item M. Aguena, C. Avestruz, C. Combet, S. Fu, R. Herbonnet, {\bf A. I. Malz}, M. Penna-Lima, M. Ricci, S. D. P. Vitenti, %et al.
L. Baumont, H. Fan, M. Fong, M. Ho, M. Kirby, C. Payerne, D. Boutigny, B. Lee, B. Liu, T. McClintock, H. Miyatake, C. Sifón, A. von der Linden, H. Wu, M. Yoon. 
2021. MNRAS 508 4 6092. \doi{10.1093/mnras/stab2764}{CLMM: a LSST-DESC Cluster weak Lensing Mass Modeling library for cosmology}
	\descr{{\bf Lead author}: conceptualization, funding acquisition, methodology, project administration, software, validation, writing}% (original draft)}% \& review/editing)}
	
\item B. Dey, J.A. Newman, B.H. Andrews, R. Izbicki, A.B. Lee, D. Zhao, M.M. Rau, {\bf A.I. Malz}. 
2021. Fourth Workshop on Machine Learning and the Physical Sciences NeurIPS. \arxiv{2110.15209}{Re-calibrating Photometric Redshift Probability Distributions Using Feature-space Regression}
\descr{Contributor: conceptualization, methodology, supervision, writing}
%\item B. Dey, B. Andrews, J.A. Newman, A.B. Lee, D. Zhao, R. Izbicki, \textbf{A.I. Malz}, A. Campos, M. Stanley. 2021. {\em submitted to NeurIPS Machine Learning and the Physical Sciences.} {Re-calibrating Probability Estimates using Local Coverage}
%	\descr{Contributor: conceptualization, data curation, investigation, methodology, software, supervision}

\item J. Zuntz, F. Lanusse, \textbf{A.I. Malz}, A.H. Wright, A. Slosar, et al. 2021. OJA 4. \doi{10.21105/astro.2108.13418} {The LSST-DESC 3x2pt Tomography Optimization Challenge}
\descr{{\bf Lead author}: conceptualization, formal analysis, methodology, visualization, writing}% (original draft)}% \& review/editing)}

\item {\bf A.I. Malz}. 2020. PRD 103 083502. \doi{10.1103/PhysRevD.103.083502}{How NOT to obtain the redshift distribution from probabilistic redshift estimates}
	\descr{{\bf Sole author}}
	
%	\item LSST-DESC, et al. (incl. {\bf A.I. Malz}) 2020. {\em DESC Note.}  \doi{10.5281/zenodo.4004760}{The LSST-DESC Science Roadmap}
%		\descr{Contributor: conceptualization, project administration, writing}% (original draft)}% \& review/editing)}

\item B. Moews, M.S. Schmitz, A.J. Lawler, J. Zuntz, {\bf A.I. Malz}, R.S. de Souza, R. Vilalta, A. Krone-Martins, E.E.O. Ishida. 2020. MNRAS 500 1 859. \doi{10.1093/mnras/staa3204}{Ridges in the Dark Energy Survey for cosmic trough identification}
	\descr{Contributor: conceptualization, methodology, writing}% (original draft)}% \& review/editing)}
  
\item S.J. Schmidt, {\bf A.I. Malz}, J.Y.H. Soo, %et al.
I.A. Almosallam, M. Brescia, S. Cavuoti, J. Johen-Tanugi, A.J. Connolly, J. DeRose, P.E. Freeman, M.L. Graham, K.G. Iyer, M.J. Jarvis, J.B. Kalmbach, E. Kovacs, A.B. Lee, G. Longo, C.B. Morrison, J.A. Newman, E. Nourbakhsh, E. Nuss, T. Pospisil, H. Tranin, R.H. Wechsler, R. Zhou, R. Izbicki. 
2020. MNRAS 499 2 1587. \doi{10.1093/mnras/staa2799}{Evaluation of probabilistic photometric redshift estimation approaches for LSST}
  \descr{{\bf Lead author}: conceptualization, formal analysis, investigation, methodology, project administration, software, supervision, validation, visualization, writing}% (original draft)}% \& review/editing)}

\item N. Kennamer, E.E.O. Ishida, S. Gonzalez-Gaitan, R.S. de Souza, A. Ihler, K. Ponder, R. Vilalta, A. Moller, D.O. Jones, M. Dai, A. Krone-Martins, B. Quint, S. Sreejitch, {\bf A.I.Malz}, L. Galbany. 2020. IEEE Symposium Series on
Computational Intelligence. \arxiv{2010.05941}{Active learning with RESSPECT: Resource allocation for extragalactic astronomical transients}
  \descr{Contributor: conceptualization, methodology}

\item N. Dalmasso, T. Pospisil, A.B. Lee, R. Izbicki, P.E. Freeman, {\bf A.I. Malz}. 2019. As. \& Com. 20 100362. \doi{10.1016/j.ascom.2019.100362}{Conditional Density Estimation Tools in Python and R with Applications to Photometric Redshifts and Likelihood-Free Cosmological Inference}
  \descr{Contributor: data curation, writing}% (original draft)}% \& review/editing)}

\item B. Moews, R.S. de Souza, E.E.O. Ishida, {\bf A.I. Malz}, C. Heneka, R. Vilalta, J. Zuntz. 2019. PRD 99 123529. \doi{10.1103/PhysRevD.99.123529}{Stress testing the dark energy equation of state imprint on supernova data}
  \descr{Contributor: conceptualization, formal analysis, investigation, methodology, validation, writing}% (original draft)}% \& review/editing)}

\item T. Cantat-Gaudin, A. Krone-Martins, N. Sedaghat, A. Farahi, R.S. de Souza, R. Skalidis, {\bf A.I. Malz}, S. Macedo, B. Moews, C. Jordi, A. Moitinho, A. Castro-Ginard, E.E.O. Ishida, C. Heneka, A. Boucaud, A.M.M. Trindade. 2019. A\&A 624 A126. \doi{10.1051/0004-6361/201834453}{Gaia DR2 unravels incompleteness of nearby cluster population: New open clusters in the direction of Perseus}
  \descr{Contributor: conceptualization, writing}% (original draft)}% \& review/editing)}

\item {\bf A.I. Malz}, R. Hlo{\v z}ek, %et al.
T. Allam Jr., A. Bahmanyar, R. Biswas, M. Dai, L. Galbany, E.E.O. Ishida, S.W. Jha, D.O. Jones, R. Kessler, M. Lochner, A.A. Mahabal, K.S. Mandel, J.R. Martinez-Galarza, J.D. McEwen, D. Muthukrishna, G. Narayan, H.V. Peiris, C.M. Peters, K. Ponder, C.N. Setzer. 
2019. AJ 158 5 171. \doi{10.3847/1538-3881/ab3a2f}{The Photometric LSST Astronomical Time-series Classification Challenge (PLAsTiCC): Selection of a performance metric for classification probabilities balancing diverse science goals}
  \descr{{\bf Lead author}: conceptualization, data curation, formal analysis, investigation, methodology, project administration, software, supervision, validation, visualization, writing}% (original draft)}% \& review/editing)}

%	\item T. Allam Jr., A. Bahmanyar, R. Biswas, M. Dai, L. Galbany, R. Hlo{\v z}ek, E.E.O. Ishida, S.W. Jha, D.O. Jones, R. Kessler, M. Lochner, A.A. Mahabal, {\bf A.I. Malz}, K.S. Mandel, J.R. Martinez-Galarza, J.D. McEwen, D. Muthukrishna, G. Narayan, H.V. Peiris, C.M. Peters, K. Ponder, C.N. Setzer. {\em LSST-DESC Research Note.} 2018. \arxiv{1810.00001}{The Photometric LSST Astronomical Time-series Classification Challenge (PLAsTiCC): Data set}
%  		\descr{Contributor: conceptualization, methodology, software}%, writing (review/editing)}

\item C. Chang, M. Wang, S. Dodelson, T. Eifler, C. Heymans, M. Jarvis, M.J. Jee, S. Joudaki, E. Krause, {\bf A.I. Malz}, R. Mandelbaum, I. Mohammed, M. Schneider, M. Simet, M.A. Troxel, J. Zuntz. 2018. MNRAS 482 3 3696. \doi{10.1093/mnras/sty2902}{A Unified Analysis of Four Cosmic Shear Surveys}
  \descr{Contributor: methodology, writing}% (original draft)}% \& review/editing)}

\item {\bf A.I. Malz}, P.J. Marshall, %et al.
M.L. Graham, S.J. Schmidt, J. DeRose, R. Wechsler. 
2018. AJ 156 0 35. \doi{10.3847/1538-3881/aac6b5}{Approximating photo-z PDFs for large surveys}
  \descr{{\bf Lead author}: conceptualization, data curation, formal analysis, funding acquisition, investigation, methodology, software, validation, visualization, writing}% (original draft)}% \& review/editing)}
  
%  	\item P.J. Marshall, et al. (incl. {\bf A.I. Malz}) 2017. {\em whitepaper.} \arxiv{1708.04058}{Science-Driven Optimization of the LSST Observing Strategy}
%  	\descr{Contributor: conceptualization, methodology, writing}% (original draft)}% \& review/editing)}

\item A.S. Leung, V. Acquaviva, E. Gawiser, R. Ciardullo, E. Komatsu, {\bf A.I. Malz}, G.R. Zeimann, %et.al.
J.S. Bridge, N. Drory, J.J Feldmeier, S.L. Finkelstein, K. Gebhardt, C. Gronwall, A. Hagen, G.J. Hill, D.P. Schneider. 
2017. ApJ 843 2 130. \doi{10.3847/1538-4357/aa71af}{Bayesian Redshift Classification of Emission-Line Galaxies with Photometric Equivalent Widths}
  \descr{Contributor: conceptualization}%, writing (review/editing)}

\item J.S. Bridge, C. Gronwall, R. Ciardullo, A. Hagen, G. Zeimann, {\bf A.I. Malz}, V. Acquaviva, D.P. Schneider, N. Drory, K. Gebhardt, S. Jogee. 2015. ApJ 799 2 205. \doi{10.1088/0004-637X/799/2/205}{Physical and Morphological Properties of [O II] Emitting Galaxies in the HETDEX Pilot Survey}
  \descr{Contributor: conceptualization, methodology}%, writing (review/editing)}

\item R. Ciardullo, G.R. Zeimann, C. Gronwall, H. Gebhardt, D.P. Schneider, A. Hagen, {\bf A.I. Malz}, G.A. Blanc, G.J. Hill, N. Drory, E. Gawiser. 2014. ApJ 796 1 64. \doi{10.1088/0004-637X/796/1/64}{HST Emission Line Galaxies at z \~ 2: The Ly-alpha Escape Fraction}
  \descr{Contributor: conceptualization, methodology}%, writing (review/editing)}

\item A. Hagen, R. Ciardullo, C. Gronwall, V. Acquaviva, J. Bridge, G.R. Zeimann, G.A. Blanc, N.A. Bond, S.L. Finkelstein, M. Song, E. Gawiser, D.B. Fox, H. Gebhardt, {\bf A.I. Malz}, D.P. Schneider, N. Drory, K. Gebhardt, G.J. Hill. 2014. ApJ 786 1 59. \doi{10.1088/0004-637X/786/1/59}{Spectral Energy Distribution Fitting of HETDEX Pilot Survey Lyman-alpha Emitters in COSMOS and GOODS-N}
  \descr{Contributor: conceptualization, methodology}%, writing (review/editing)}
  
\end{list}


%\clearpage

%\malzheading{Unrefereed publications}%
%\nopagebreak\begin{list}{}{\malzlist}
	%\end{list}
\malzheading{Published Software} 
	{\fontsize{9pt}{5pt}\selectfont\textcolor{grey}{All of AIM's code, including work in progress, is publicly available on GitHub; these have formal releases with DOIs.}\par}
	% at \hyperlink{https://github.com/aimalz}{github.com/aimalz} or \hyperlink{https://github.com/LSSTDESC}{github.com/LSSTDESC}.}\par}
% add in licenses, summary of software, URL
\nopagebreak\begin{list}{}{\malzlist}

%Conceptualization
%Data curation
%Formal analysis
%Funding acquisition
%Investigation
%Methodology
%Project administration
%Resources
%Software
%Supervision
%Validation
%Visualization
%Writing - original draft.
%Writing - review & editing

% recidivator/pollock
% ReSSpect

\item LSST-DESC RAIL Topical Team (led by {\bfseries{A.I. Malz}}). 2022. \href{https://github.com/LSSTDESC/qp}{``{\tt qp}"}
\descr{{\bf Lead author}: conceptualization, methodology, project administration, software, supervision, validation, writing (documentation)}

\item LSST-DESC RAIL Topical Team (led by {\bfseries{A.I. Malz}}). 2022. \doi{10.5281/zenodo.7076131}{\tt RAIL}.
\descr{{\bf Lead author}: conceptualization, methodology, project administration, software, supervision, validation, writing (documentation)}

\item LSST-DESC CLMassMod Team (led by {\bf A.I. Malz}). 2021. \doi{10.5281/zenodo.5596167}{\tt CLMM}.
\descr{{\bf Lead author}: conceptualization, funding acquisition, methodology, project administration, software, supervision, writing (documentation)}

\item {\bf A.I. Malz}. 2020. \doi{10.5281/zenodo.4085252}{\tt chippr}. %\deemph{(Cosmological Hierarchical Inference with Probabilistic Photometric Redshifts: \textit{implementation of the CHIPPR method of Malz \& Hogg 2021})}
\descr{\bf Sole author}

\item {\bf A.I. Malz}, et al. 2019. \doi{10.5281/zenodo.3352639}{\tt ProClaM}. %\deemph{(Probabilistic Classification Metrics: \textit{library for evaluating metrics of probabilistic classifications})}
\descr{{\bf Lead author}: conceptualization, methodology, software, validation, visualization, writing (documentation)}

\item B. Brewer, T.K. Leung \& {\bf A.I. Malz}. 2018. \doi{10.5281/zenodo.1410782}{\tt StarStudded}. %\deemph{(\textit{package for generating probabilistic catalogs of crowded stellar fields})}
\descr{Contributor: software}

\item {\bf A.I. Malz} \& P.J. Marshall. 2017. \doi{10.5281/zenodo.1133465}{\tt qp}. %\deemph{(Quantile Parameterization: \textit{toolkit for handling diverse parameterizations of univariate probability density functions})}
\descr{{\bf Lead author}: conceptualization, methodology, software, validation, visualization, writing (documentation)}
\end{list}
% \item
% Foreman-Mackey,~D., Hogg,~D.~W., Lang,~D., \& Goodman,~J., 2012,
% {\project{emcee} codebase}, MIT License,
% an adaptive ensemble sampler
% (\url{http://danfm.ca/emcee/}).

%\clearpage

\malzheading{Non-standard Publications}
% add in licenses, summary of software, URL
\nopagebreak\begin{list}{}{\malzlist}
	
	\item K. Breivik, et al. (incl. {\bf A.I. Malz}) 2022. {\em whitepaper.} \arxiv{2208.02781}{From Data to Software to Science with the Rubin Observatory LSST }
		\descr{Contributor: conceptualization, investigation, writing}% (original draft)}% \& review/editing)}
	
	\item LSST-DESC, et al. (incl. {\bf A.I. Malz}) 2020. {\em LSST-DESC Research Note.}  \doi{10.5281/zenodo.5527255}{The LSST-DESC Science Roadmap}% https://doi.org/10.5281/zenodo.3547566\doi{10.5281/zenodo.4004760}
		\descr{Contributor: conceptualization, project administration, writing}% (original draft)}% \& review/editing)}
	
	\item T. Allam Jr., A. Bahmanyar, R. Biswas, M. Dai, L. Galbany, R. Hlo{\v z}ek, E.E.O. Ishida, S.W. Jha, D.O. Jones, R. Kessler, M. Lochner, A.A. Mahabal, {\bf A.I. Malz}, K.S. Mandel, J.R. Martinez-Galarza, J.D. McEwen, D. Muthukrishna, G. Narayan, H.V. Peiris, C.M. Peters, K. Ponder, C.N. Setzer. {\em LSST-DESC Research Note.} 2018. \arxiv{1810.00001}{The Photometric LSST Astronomical Time-series Classification Challenge (PLAsTiCC): Data set}
	\descr{Contributor: conceptualization, methodology, software}%, writing (review/editing)}
	
	\item {\bf A.I. Malz}, et al. 2018. \doi{10.5281/zenodo.6382752}{Dance Your Ph.D. 2018/9: Probabilistic methods for cosmological analysis with uncertainty-dominated data} 
	\deemph{\href{https://youtu.be/vKs3PYqZWg8}{(educational music video)}}
		\descr{{\bf Lead author}: conceptualization, funding acquisition, methodology (choreography), project administration (production), resources (costumes), software (video editing \& web maintenance), supervision, visualization}
	
	\item P.J. Marshall, et al. (incl. {\bf A.I. Malz}) 2017. {\em whitepaper.}  \arxiv{1708.04058}{Science-Driven Optimization of the LSST Observing Strategy}
		\descr{Contributor: conceptualization, methodology, writing}% (original draft)}% \& review/editing)}
	
	\item {\bf A.I. Malz}. 2017. Cooper Square Review. \href{http://coopersquarereview.org/post/going-nowhere-fast/}{``Going nowhere fast''} \deemph{(science communication essay)}
		\descr{\bf Sole author}
\end{list}


%\clearpage
\malzheading{Citeable Presentations}
% add in licenses, summary of software, URL
\nopagebreak\begin{list}{}{\malzlist}
	
% other LINCC AAS 241 posters!

	\item {\bf A.I. Malz} \& the Extended PLAsTiCC (ELAsTiCC) Team. 2023. American Astronomical Society, AAS Meeting \#241, id. 117.04 ``ELAsTiCC: Metrics of probabilistic classifications of the alert stream" \deemph{(contributed talk)}
	%	\descr{{\bf Lead author}: conceptualization, formal analysis, investigation, methodology, project administration, software, validation, visualization, writing}
	
	\item {\bf A.I. Malz} \& the LSST-DESC RAIL Team. 2023. American Astronomical Society, AAS Meeting \#241, Astronomy and Cloud Computing Special Session, id. 358.01. ``All aboard! A LINCC Framework for extragalactic science using RAIL" \deemph{(contributed poster)}
	%	\descr{{\bf Lead author}: conceptualization, formal analysis, investigation, methodology, project administration, software, validation, visualization, writing}
	
	\item {\bf A.I. Malz}. 2021. American Astronomical Society, AAS Meeting \#238, Machine Learning in Astronomy Meeting-in-a-Meeting, id. 103.02. ``Proceed with caution: how, and how not, to use machine learning to probe cosmology" \deemph{(invited talk)}
	%	\descr{{\bf Sole author}}
	
	\item {\bf A.I. Malz}, F. Lanusse, J.F. Crenshaw, M.L. Graham. 2021. American Astronomical Society, AAS Meeting \#238, id. 230.04. ``\texttt{TheLastMetric}: an information-based observing strategy metric for photometric redshifts, cosmology, and more" \deemph{(contributed poster)}
%	\descr{{\bf Lead author}: conceptualization, formal analysis, investigation, methodology, project administration, software, validation, visualization, writing}
%	 (original draft)}% \& review/editing)}
	
	\item J.F. Crenshaw, J.B. Kalmbach, {\bf A.I. Malz}, A.J. Connolly. 2021. American Astronomical Society, AAS Meeting \#238, id. 230.01. ``\texttt{PZFlow}: normalizing flows for cosmology, with applications to forward modeling galaxy photometry" \deemph{(contributed poster)}
%	\descr{Contributor: supervision, validation}
	
	\item {\bf A.I. Malz}. 2021. American Astronomical Society, AAS Meeting \#237, LSST-DESC Special Session, id. 443.05. ``The DESC Photometric Redshifts Working Group: Challenges \& Opportunities'' \deemph{(contributed talk)}
%	\descr{{\bf Sole author}}
	
	\item {\bf A.I. Malz}. 2019. American Astronomical Society, AAS Meeting \#233, Surveys \& Large Programs, id. 313.05D. ``Probabilistic data analysis methods for large photometric surveys'' \deemph{(contributed talk)}
%	\descr{{\bf Sole author}}
	%
	\item {\bf A.I. Malz}. 2019. American Astronomical Society, AAS Meeting \#233, Larger Efforts in Education \& Public Outreach, id. 212.05. ``The Photometric LSST Astronomical Time Series Classification Challenge (PLAsTiCC): challenge design and evaluation criteria” \deemph{(contributed talk)}
%	\descr{{\bf Sole author}}
	
	\item C.M. Peters, {\bf A.I. Malz} \& R. Hlozek. 2018. American Astronomical Society, AAS Meeting \#231, id. 245.03. ``Supernova Cosmology Inference with Probabilistic Photometric Redshifts'' \deemph{(contributed poster)}
%	\descr{{\bf Lead author}: conceptualization, data curation, formal analysis, investigation, methodology, software, validation, visualization, writing}
%	 (original draft)}% \& review/editing)}
	
	\item {\bf A.I. Malz} \& S. Shandera. 2014. American Astronomical Society, AAS Meeting \#223, id. 456.04. ``Probing Gravity in the High-Redshift Universe with HETDEX'' \deemph{(contributed poster)}
%	\descr{{\bf Lead author}; conceptualization, data curation, formal analysis, investigation, methodology, visualization, writing}
%	 (original draft)}% \& review/editing)}
	
	\item {\bf A.I. Malz}, R. Rich \& S. Lepine. 2009. American Astronomical Society, AAS Meeting \#213, id. 602.04. ``Low-mass Binaries in the Galactic Halo Resolved by Adaptive Optics'' \deemph{(contributed poster)}
%	\descr{{\bf Lead author}; formal analysis, funding acquisition, investigation, writing}
%	 (original draft)}% \& review/editing)}
\end{list}
