%conceptualization, data curation, formal analysis, funding acquisition, investigation, methodology, project administration, resources, software, supervision, validation, visualization, writing

\begin{etaremune}


% Alice's paper
%\item RAIL v1
%\item ELAsTiCC metrics
%\item ELAsTiCC release note
%\item lost and found
%\item recidivator/pollock?
%\item SCIPPR

% DeepDISC incubator

\item B. Scott, {\bf A.I. Malz}, R. Sorba. {\em submitted to ApJ 30 September 2024.} \arxiv{2409.20443}{A holistic exploration of the potentially recoverable redshift information of Stage IV photometric galaxy surveys}
\descr{{\color{black} \bf Lead author}: conceptualization, formal analysis, investigation, methodology, project administration, software, supervision validation, visualization, writing}

\item {\bf A.I. Malz}, F. Lanusse, J.F. Crenshaw, B. Scott, M.L. Graham, X. Li. {\em accepted to ApJS 17 September 2024.} \arxiv{2104.08229}{An information-based metric for observing strategy optimization, demonstrated in the context of photometric redshifts with applications to cosmology}
\descr{{\color{black} \bf Lead author}: conceptualization, data curation, formal analysis, funding acquisition, investigation, methodology, software, validation, visualization, writing}% (original draft)}% \& review/editing)}

\item I. Mendoza, A. Torchylo, T. Sainrat, A. Guinot, A. Boucaud, M. Paillasa, C. Avestruz, P. Adari, E. Aubourg, B. Biswas, J. Buchanan, P. Burchat, C. Doux, R. Joseph, S. Kamath, {\bf A.I. Malz}, G. Merz, H. Miyatake, C. Roucelle, T. Zhang, LSST-DESC. {\em submitted 11 September 2024.} \arxiv{2409.06986}{The Blending ToolKit: A simulation framework for evaluation of galaxy detection and deblending}
\descr{{\bf Contributor}: validation, visualization}

\item Q. Hang, B. Joachimi, E. Charles, J.F. Crenshaw, P. Larsen, {\bf A.I. Malz}, S. Schmidt, Z. Yan, T. Zhang, LSST-DESC. {\em submitted to MNRAS 24 August 2024.} \arxiv{2409.02501}{Impact of survey spatial variability on galaxy redshift distributions and the cosmological 3×2-point statistics for the Rubin Legacy Survey of Space and Time (LSST)}
\descr{{\bf Contributor}: conceptualization, funding acquisition, software, writing}% (review/editing)}

\item K.M. de Soto, A. Villar, E. Berger, S. Gomez, G. Hosseinzadeh, D. Branton, S. Campos, M. DeLucchi, J. Kubica, O. Lynn, K. Malanchev, {\bf A.I. Malz}. {\em accepted to AAS Journals 25 July 2024.} \arxiv{2403.07975}{Superphot+: Realtime Fitting and Classification of Supernova Light Curves}
\descr{{\bf Contributor}: conceptualization, methodology}% (review/editing)}

\item J.F. Crenshaw, J.B. Kalmbach, A. Gagliano, Z. Yan, A.J. Connolly, {\bf A.I. Malz}, S.J. Schmidt. {\em submitted to AJ 8 May 2024.} \arxiv{2405.04740}{Probabilistic Forward Modeling of Galaxy Catalogs with Normalizing Flows}
\descr{{\bf Contributor}: conceptualization, funding acquisition, validation}

\item J. Lee, M. Sako, R. Kessler, {\bf A.I. Malz}. {\em submitted to ApJ 5 May 2024.} \arxiv{2405.04522}{Astrometric Redshifts of Supernovae}
\descr{{\bf Contributor}: data curation, software, writing}

\item {\bf A.I. Malz}, M. Dai, K.A. Ponder, E.E.O. Ishida, S. Gonzalez-Gaitain, R. Durgesh, A. Krone-Martins, R.S. de Souza, N. Kennamer, S. Sreejith, L. Galbany. {\em accepted to A\&A 2 May 2024.} \arxiv{2305.14421}{Are classification metrics good proxies for SN Ia cosmological constraining power?}
\descr{{\color{black} \bf Lead author}: conceptualization, formal analysis, investigation, methodology, software, validation, visualization, writing}% - original draft, writing - review \& editing)}

\item  D. Oldag, M. DeLucchi, W. Beebe, D. Branton, S. Campos, C.O. Chandler, C. Christofferson, A. Connolly, J. Kubica, O. Lynn, K. Malanchev, {\bf A.I. Malz}, R. Mandelbaum, S. McGuire, C. Wenneman. 2024. RNAAS 8 5 141. \doi{10.3847/2515-5172/ad4da1}{A Python Project Template for Healthy Scientific Software}
\descr{{\bf Contributor}: conceptualization, software, writing}

\item I. Moskowitz, E. Gawiser, J.F. Crenshaw, B.H. Andrews, {\bf A.I. Malz}, S. Schmidt. 2024. ApJL 967 L6. \doi{10.3847/2041-8213/ad4039}{Improving Photometric Redshift Estimates with Training Sample Augmentation}
\descr{{\bf Contributor}: software}

\item A. Gagliano, G. Contardo, D. Foreman-Mackey, {\bf A.I. Malz}, P.D. Aleo. 2023. ApJ 954 6. \doi{10.3847/1538-4357/ace326}{First Impressions: Early-Time Classification of Supernovae using Host Galaxy Information and Shallow Learning}
\descr{{\bf Contributor}: data curation, resources, software, writing}% (review/editing)}

\item R. Hlo{\v z}ek, {\bf A.I. Malz}, K.A. Ponder, M. Dai, G. Narayan, E.E.O. Ishida,% et al.
T. Allam Jr., A. Bahmanyar, R. Biswas, L. Galbany, S.W. Jha, D.O. Jones, R. Kessler, M. Lochner, A.A. Mahabal, K.S. Mandel, J.R. Martinez-Galarza, J.D. McEwen, D. Muthukrishna, H.V. Peiris, C.M. Peters, C.N. Setzer. 2023. ApJS 267 25. \doi{10.3847/1538-4365/accd6a}{Results of the Photometric LSST Astronomical Time-series Classification Challenge (PLAsTiCC)}
\descr{{\color{black} \bf Lead author}: conceptualization, formal analysis, investigation, methodology, visualization, writing}% (original draft)}% \& review/editing)}

\item  M. Lokken, A. Gagliano, G. Narayan, R. Hlo{\v z}ek, R. Kessler, J.F. Crenshaw, L. Salo, C.S. Alves, D. Chatterjee, M. Vincenzi, {\bf A.I. Malz}. 2023. MNRAS 520 2. \doi{10.1093/mnras/stad302}{The Simulated Catalogue of Optical Transients and Correlated Hosts (SCOTCH)}
\descr{{\bf Contributor}: conceptualization, data curation, methodology}% (original draft)}% \& review/editing)}

\textit{Please pardon the apparent gap in publications as a result of the global pandemic limiting collaboration opportunities during the preceding two years.}
% I was 100\% remote and effectively cut off from the in-person interactions that are so crucial to my collaborative approach to research from early 2020 until mid 2022. I worked through many ideas I'd come up with before the pandemic but started to run out of fresh material without exposure to new ideas. Once I was back in an in-person position with more opportunities to catalyze new ideas, it took about a year for the new project concepts to mature into publications.}

\item N. Stylianou, {\bf A.I. Malz}, P. Hatfield, J.F. Crenshaw, J. Gschwend. 2021. PASP 134 1034. \doi{10.1088/1538-3873/ac59bf}{The sensitivity of GPz estimates of photo-z posterior PDFs to realistically complex training set imperfections}
\descr{{\color{black} \bf Lead author}: conceptualization, data curation, formal analysis, funding acquisition, investigation, methodology, software, supervision, validation, visualization, writing}% (original draft)}% \& review/editing)}

\item {\bf A.I. Malz}, D.W. Hogg. 2021. ApJ 928 127. \doi{10.3847/1538-4357/ac062f}{How to obtain the redshift distribution from probabilistic redshift estimates}
\descr{{\color{black} \bf Lead author}: conceptualization, data curation, formal analysis, funding acquisition, investigation, methodology, software, validation, visualization, writing}% (original draft)}% \& review/editing)}

\item M. Aguena, C. Avestruz, C. Combet, S. Fu, R. Herbonnet, {\bf A. I. Malz}, M. Penna-Lima, M. Ricci, S. D. P. Vitenti, %et al.
L. Baumont, H. Fan, M. Fong, M. Ho, M. Kirby, C. Payerne, D. Boutigny, B. Lee, B. Liu, T. McClintock, H. Miyatake, C. Sifón, A. von der Linden, H. Wu, M. Yoon. 
2021. MNRAS 508 4 6092. \doi{10.1093/mnras/stab2764}{CLMM: a LSST-DESC Cluster weak Lensing Mass Modeling library for cosmology}
\descr{{\color{black} \bf Lead author}: conceptualization, funding acquisition, methodology, project administration, software, validation, writing}% (original draft)}% \& review/editing)}

\item B. Dey, J.A. Newman, B.H. Andrews, R. Izbicki, A.B. Lee, D. Zhao, M.M. Rau, {\bf A.I. Malz}. 
2021. Fourth Workshop on Machine Learning and the Physical Sciences NeurIPS. \arxiv{2110.15209}{Re-calibrating Photometric Redshift Probability Distributions Using Feature-space Regression}
\descr{{\bf Contributor}: conceptualization, methodology, supervision, writing}
%\item B. Dey, B. Andrews, J.A. Newman, A.B. Lee, D. Zhao, R. Izbicki, \textbf{A.I. Malz}, A. Campos, M. Stanley. 2021. {\em submitted to NeurIPS Machine Learning and the Physical Sciences.} {Re-calibrating Probability Estimates using Local Coverage}
%	\descr{Contributor: conceptualization, data curation, investigation, methodology, software, supervision}

\item J. Zuntz, F. Lanusse, \textbf{A.I. Malz}, A.H. Wright, A. Slosar, %et al. 
B. Abolfathi, D. Alonso, A. Bault, C.R. Bom, M. Brescia, A. Broussard, J.-E. Campagne, S. Cavuoti, E.S. Cypriano, B.M.O. Fraga, E. Gawiser, E.J. Gonzalez, D. Green, P. Hatfield, K. Iyer, D. Kirkby, A. Nicola, E. Nourbakhsh, A. Park, G. Teixeira, K. Heitmann, E. Kovacs, Y.-Y. Mao. 2021. OJA 4. \doi{10.21105/astro.2108.13418} {The LSST-DESC 3x2pt Tomography Optimization Challenge}
\descr{{\color{black} \bf Lead author}: conceptualization, formal analysis, methodology, visualization, writing}% (original draft)}% \& review/editing)}

\item {\bf A.I. Malz}. 2020. PRD 103 083502. \doi{10.1103/PhysRevD.103.083502}{How NOT to obtain the redshift distribution from probabilistic redshift estimates}
\descr{{\color{black} \bf Sole author}: conceptualization, formal analysis, investigation, methodology, project administration, resources, writing}

%	\item LSST-DESC, et al. (incl. {\bf A.I. Malz}) 2020. {\em DESC Note.}  \doi{10.5281/zenodo.4004760}{The LSST-DESC Science Roadmap}
%		\descr{Contributor: conceptualization, project administration, writing}% (original draft)}% \& review/editing)}

\item B. Moews, M.S. Schmitz, A.J. Lawler, J. Zuntz, {\bf A.I. Malz}, R.S. de Souza, R. Vilalta, A. Krone-Martins, E.E.O. Ishida. 2020. MNRAS 500 1 859. \doi{10.1093/mnras/staa3204}{Ridges in the Dark Energy Survey for cosmic trough identification}
\descr{{\bf Contributor}: conceptualization, methodology, writing}% (original draft)}% \& review/editing)}

\item S.J. Schmidt, {\bf A.I. Malz}, J.Y.H. Soo, %et al.
I.A. Almosallam, M. Brescia, S. Cavuoti, J. Johen-Tanugi, A.J. Connolly, J. DeRose, P.E. Freeman, M.L. Graham, K.G. Iyer, M.J. Jarvis, J.B. Kalmbach, E. Kovacs, A.B. Lee, G. Longo, C.B. Morrison, J.A. Newman, E. Nourbakhsh, E. Nuss, T. Pospisil, H. Tranin, R.H. Wechsler, R. Zhou, R. Izbicki. 
2020. MNRAS 499 2 1587. \doi{10.1093/mnras/staa2799}{Evaluation of probabilistic photometric redshift estimation approaches for LSST}
\descr{{\color{black} \bf Lead author}: conceptualization, formal analysis, investigation, methodology, project administration, software, supervision, validation, visualization, writing}% (original draft)}% \& review/editing)}

\item N. Kennamer, E.E.O. Ishida, S. Gonzalez-Gaitan, R.S. de Souza, A. Ihler, K. Ponder, R. Vilalta, A. Moller, D.O. Jones, M. Dai, A. Krone-Martins, B. Quint, S. Sreejitch, {\bf A.I. Malz}, L. Galbany. 2020. IEEE Symposium Series on
Computational Intelligence. \arxiv{2010.05941}{Active learning with RESSPECT: Resource allocation for extragalactic astronomical transients}
\descr{{\bf Contributor}: conceptualization, methodology}

\item N. Dalmasso, T. Pospisil, A.B. Lee, R. Izbicki, P.E. Freeman, {\bf A.I. Malz}. 2019. As. \& Com. 20 100362. \doi{10.1016/j.ascom.2019.100362}{Conditional Density Estimation Tools in Python and R with Applications to Photometric Redshifts and Likelihood-Free Cosmological Inference}
\descr{{\bf Contributor}: data curation, writing}% (original draft)}% \& review/editing)}

\item B. Moews, R.S. de Souza, E.E.O. Ishida, {\bf A.I. Malz}, C. Heneka, R. Vilalta, J. Zuntz. 2019. PRD 99 123529. \doi{10.1103/PhysRevD.99.123529}{Stress testing the dark energy equation of state imprint on supernova data}
\descr{{\bf Contributor}: conceptualization, formal analysis, investigation, methodology, validation, writing}% (original draft)}% \& review/editing)}

\item T. Cantat-Gaudin, A. Krone-Martins, N. Sedaghat, A. Farahi, R.S. de Souza, R. Skalidis, {\bf A.I. Malz}, S. Macedo, B. Moews, C. Jordi, A. Moitinho, A. Castro-Ginard, E.E.O. Ishida, C. Heneka, A. Boucaud, A.M.M. Trindade. 2019. A\&A 624 A126. \doi{10.1051/0004-6361/201834453}{Gaia DR2 unravels incompleteness of nearby cluster population: New open clusters in the direction of Perseus}
\descr{{\bf Contributor}: conceptualization, writing}% (original draft)}% \& review/editing)}

\item {\bf A.I. Malz}, R. Hlo{\v z}ek, %et al.
T. Allam Jr., A. Bahmanyar, R. Biswas, M. Dai, L. Galbany, E.E.O. Ishida, S.W. Jha, D.O. Jones, R. Kessler, M. Lochner, A.A. Mahabal, K.S. Mandel, J.R. Martinez-Galarza, J.D. McEwen, D. Muthukrishna, G. Narayan, H.V. Peiris, C.M. Peters, K. Ponder, C.N. Setzer. 
2019. AJ 158 5 171. \doi{10.3847/1538-3881/ab3a2f}{The Photometric LSST Astronomical Time-series Classification Challenge (PLAsTiCC): Selection of a performance metric for classification probabilities balancing diverse science goals}
\descr{{\color{black} \bf Lead author}: conceptualization, data curation, formal analysis, investigation, methodology, project administration, software, supervision, validation, visualization, writing}% (original draft)}% \& review/editing)}

%	\item T. Allam Jr., A. Bahmanyar, R. Biswas, M. Dai, L. Galbany, R. Hlo{\v z}ek, E.E.O. Ishida, S.W. Jha, D.O. Jones, R. Kessler, M. Lochner, A.A. Mahabal, {\bf A.I. Malz}, K.S. Mandel, J.R. Martinez-Galarza, J.D. McEwen, D. Muthukrishna, G. Narayan, H.V. Peiris, C.M. Peters, K. Ponder, C.N. Setzer. {\em LSST-DESC Research Note.} 2018. \arxiv{1810.00001}{The Photometric LSST Astronomical Time-series Classification Challenge (PLAsTiCC): Data set}
%  		\descr{Contributor: conceptualization, methodology, software}%, writing (review/editing)}

\item C. Chang, M. Wang, S. Dodelson, T. Eifler, C. Heymans, M. Jarvis, M.J. Jee, S. Joudaki, E. Krause, {\bf A.I. Malz}, R. Mandelbaum, I. Mohammed, M. Schneider, M. Simet, M.A. Troxel, J. Zuntz. 2018. MNRAS 482 3 3696. \doi{10.1093/mnras/sty2902}{A Unified Analysis of Four Cosmic Shear Surveys}
\descr{{\bf Contributor}: methodology, writing}% (original draft)}% \& review/editing)}

\item {\bf A.I. Malz}, P.J. Marshall, M.L. Graham, S.J. Schmidt, J. DeRose, R. Wechsler. 
2018. AJ 156 0 35. \doi{10.3847/1538-3881/aac6b5}{Approximating photo-z PDFs for large surveys}
\descr{{\color{black} \bf Lead author}: conceptualization, data curation, formal analysis, funding acquisition, investigation, methodology, software, validation, visualization, writing}% (original draft)}% \& review/editing)}

%  	\item P.J. Marshall, et al. (incl. {\bf A.I. Malz}) 2017. {\em whitepaper.} \arxiv{1708.04058}{Science-Driven Optimization of the LSST Observing Strategy}
%  	\descr{Contributor: conceptualization, methodology, writing}% (original draft)}% \& review/editing)}

\item A.S. Leung, V. Acquaviva, E. Gawiser, R. Ciardullo, E. Komatsu, {\bf A.I. Malz}, G.R. Zeimann, %et.al.
J.S. Bridge, N. Drory, J.J Feldmeier, S.L. Finkelstein, K. Gebhardt, C. Gronwall, A. Hagen, G.J. Hill, D.P. Schneider. 
2017. ApJ 843 2 130. \doi{10.3847/1538-4357/aa71af}{Bayesian Redshift Classification of Emission-Line Galaxies with Photometric Equivalent Widths}
\descr{{\bf Contributor}: conceptualization}%, writing (review/editing)}

\item J.S. Bridge, C. Gronwall, R. Ciardullo, A. Hagen, G. Zeimann, {\bf A.I. Malz}, V. Acquaviva, D.P. Schneider, N. Drory, K. Gebhardt, S. Jogee. 2015. ApJ 799 2 205. \doi{10.1088/0004-637X/799/2/205}{Physical and Morphological Properties of [O II] Emitting Galaxies in the HETDEX Pilot Survey}
\descr{{\bf Contributor}: conceptualization, methodology}%, writing (review/editing)}

\item R. Ciardullo, G.R. Zeimann, C. Gronwall, H. Gebhardt, D.P. Schneider, A. Hagen, {\bf A.I. Malz}, G.A. Blanc, G.J. Hill, N. Drory, E. Gawiser. 2014. ApJ 796 1 64. \doi{10.1088/0004-637X/796/1/64}{HST Emission Line Galaxies at $z \sim 2$: The Ly-alpha Escape Fraction}
\descr{{\bf Contributor}: conceptualization, methodology}%, writing (review/editing)}

\item A. Hagen, R. Ciardullo, C. Gronwall, V. Acquaviva, J. Bridge, G.R. Zeimann, G.A. Blanc, N.A. Bond, S.L. Finkelstein, M. Song, E. Gawiser, D.B. Fox, H. Gebhardt, {\bf A.I. Malz}, D.P. Schneider, N. Drory, K. Gebhardt, G.J. Hill. 2014. ApJ 786 1 59. \doi{10.1088/0004-637X/786/1/59}{Spectral Energy Distribution Fitting of HETDEX Pilot Survey Lyman-alpha Emitters in COSMOS and GOODS-N}
\descr{{\bf Contributor}: conceptualization, methodology}%, writing (review/editing)}

%\end{list}
\end{etaremune}


%\clearpage

%\malzheading{Unrefereed publications}%
%\nopagebreak\begin{list}{}{\malzlist}
%\end{list}
\malzheading{Published Software} 
{\fontsize{9pt}{5pt}\selectfont\textcolor{grey}{All of AIM's code, including work in progress, is publicly available on GitHub; these have formal releases with DOIs.}\par}
% at \hyperlink{https://github.com/aimalz}{github.com/aimalz} or \hyperlink{https://github.com/LSSTDESC}{github.com/LSSTDESC}.}\par}
% add in licenses, summary of software, URL
\nopagebreak\begin{list}{}{\malzlist}

%Conceptualization
%Data curation
%Formal analysis
%Funding acquisition
%Investigation
%Methodology
%Project administration
%Resources
%Software
%Supervision
%Validation
%Visualization
%Writing - original draft.
%Writing - review & editing

% recidivator/pollock
% ReSSpect

\item LSST-DESC RAIL Topical Team (led by {\bfseries{A.I. Malz}}). 2023. \sw{10.5281/zenodo.7017551}{RAIL}
\descr{{\color{black} {\bf Lead author}}: conceptualization, funding acquisition, methodology, project administration, software, supervision, validation, writing (documentation)}

\item LSST-DESC RAIL Topical Team (led by {\bfseries{A.I. Malz}}). 2022. \sw{10.5281/zenodo.7815296}{qp}
\descr{{\color{black} {\bf Lead author}}: conceptualization, funding acquisition, methodology, project administration, software, supervision, validation, writing (documentation)}

\item LSST-DESC CLMassMod Team (led by {\bf A.I. Malz}). 2021. \sw{10.5281/zenodo.5596167}{CLMM}
\descr{{\color{black}{\bf Lead author}}: conceptualization, funding acquisition, methodology, project administration, software, supervision, writing (documentation)}

\item {\bf A.I. Malz}. 2020. \sw{10.5281/zenodo.4085252}{chippr} %\deemph{(Cosmological Hierarchical Inference with Probabilistic Photometric Redshifts: \textit{implementation of the CHIPPR method of Malz \& Hogg 2021})}
\descr{{\color{black} \bf Sole author}: conceptualization, funding acquisition, methodology, project administration, resources, software, validation, visualization, writing (documentation)}

\item {\bf A.I. Malz}, et al. 2019. \sw{10.5281/zenodo.3352639}{ProClaM} %\deemph{(Probabilistic Classification Metrics: \textit{library for evaluating metrics of probabilistic classifications})}
\descr{{\color{black} {\bf Lead author}}: conceptualization, methodology, software, validation, visualization, writing (documentation)}

\item B. Brewer, T.K. Leung \& {\bf A.I. Malz}. 2018. \sw{10.5281/zenodo.1410782}{StarStudded} %\deemph{(\textit{package for generating probabilistic catalogs of crowded stellar fields})}
\descr{Contributor: software}

\item {\bf A.I. Malz} \& P.J. Marshall. 2017. \sw{10.5281/zenodo.1133465}{qp} %\deemph{(Quantile Parameterization: \textit{toolkit for handling diverse parameterizations of univariate probability density functions})}
\descr{{\color{black} {\bf Lead author}}: conceptualization, methodology, software, validation, visualization, writing (documentation)}
\end{list}
% \item
% Foreman-Mackey,~D., Hogg,~D.~W., Lang,~D., \& Goodman,~J., 2012,
% {\project{emcee} codebase}, MIT License,
% an adaptive ensemble sampler
% (\url{http://danfm.ca/emcee/}).

%\clearpage

\malzheading{Non-standard Publications}
% add in licenses, summary of software, URL
\nopagebreak\begin{list}{}{\malzlist}

\item K. Breivik, et al. (incl. {\bf A.I. Malz}) 2022. {\em whitepaper.} \arxiv{2208.02781}{From Data to Software to Science with the Rubin Observatory LSST }
\descr{Contributor: conceptualization, investigation, writing}% (original draft)}% \& review/editing)}

\item LSST-DESC, et al. (incl. {\bf A.I. Malz}) 2020. {\em LSST-DESC Research Note.}  \doi{10.5281/zenodo.5527255}{The LSST-DESC Science Roadmap}% https://doi.org/10.5281/zenodo.3547566\doi{10.5281/zenodo.4004760}
\descr{Contributor: conceptualization, project administration, writing}% (original draft)}% \& review/editing)}

\item T. Allam Jr., A. Bahmanyar, R. Biswas, M. Dai, L. Galbany, R. Hlo{\v z}ek, E.E.O. Ishida, S.W. Jha, D.O. Jones, R. Kessler, M. Lochner, A.A. Mahabal, {\bf A.I. Malz}, K.S. Mandel, J.R. Martinez-Galarza, J.D. McEwen, D. Muthukrishna, G. Narayan, H.V. Peiris, C.M. Peters, K. Ponder, C.N. Setzer. {\em LSST-DESC Research Note.} 2018. \arxiv{1810.00001}{The Photometric LSST Astronomical Time-series Classification Challenge (PLAsTiCC): Data set}
\descr{Contributor: conceptualization, methodology, software}%, writing (review/editing)}

\item {\bf A.I. Malz}, et al. 2018. \doi{10.5281/zenodo.6382752}{Dance Your Ph.D. 2018/9: Probabilistic methods for cosmological analysis with uncertainty-dominated data} 
\deemph{\href{https://youtu.be/vKs3PYqZWg8}{(educational music video)}}
\descr{{\color{black} {\bf Lead author}}: conceptualization, funding acquisition, methodology (choreography), project administration (production), resources (costumes), software (video editing \& web maintenance), supervision, visualization}

\item P.J. Marshall, et al. (incl. {\bf A.I. Malz}) 2017. {\em whitepaper.}  \arxiv{1708.04058}{Science-Driven Optimization of the LSST Observing Strategy}
\descr{Contributor: conceptualization, methodology, writing}% (original draft)}% \& review/editing)}

\item {\bf A.I. Malz}. 2017. Cooper Square Review. \href{https://web.archive.org/web/20191022100654/http://coopersquarereview.org/post/going-nowhere-fast/}{``Going nowhere fast''} \deemph{(science communication essay)}
\descr{{\color{black} {\bf Sole author}}: conceptualization, writing}
\end{list}


%\clearpage
\malzheading{Citeable Presentations}
% add in licenses, summary of software, URL
\nopagebreak\begin{list}{}{\malzlist}

% other LINCC AAS 241, 243 posters!

\item {\bf A.I. Malz} \& the Extended PLAsTiCC (ELAsTiCC) Team. 2023. American Astronomical Society, AAS Meeting \#241, id. 117.04 ``ELAsTiCC: Metrics of probabilistic classifications of the alert stream" \deemph{(contributed talk)}
%	\descr{{\bf Lead author}: conceptualization, formal analysis, investigation, methodology, project administration, software, validation, visualization, writing}

\item {\bf A.I. Malz} \& the LSST-DESC RAIL Team. 2023. American Astronomical Society, AAS Meeting \#241, Astronomy and Cloud Computing Special Session, id. 358.01. ``All aboard! A LINCC Framework for extragalactic science using RAIL" \deemph{(contributed poster)}
%	\descr{{\bf Lead author}: conceptualization, formal analysis, investigation, methodology, project administration, software, validation, visualization, writing}

\item {\bf A.I. Malz}. 2021. American Astronomical Society, AAS Meeting \#238, Machine Learning in Astronomy Meeting-in-a-Meeting, id. 103.02. ``Proceed with caution: how, and how not, to use machine learning to probe cosmology" \deemph{(invited talk)}
%	\descr{{\bf Sole author}}

\item {\bf A.I. Malz}, F. Lanusse, J.F. Crenshaw, M.L. Graham. 2021. American Astronomical Society, AAS Meeting \#238, id. 230.04. ``\texttt{TheLastMetric}: an information-based observing strategy metric for photometric redshifts, cosmology, and more" \deemph{(contributed poster)}
%	\descr{{\bf Lead author}: conceptualization, formal analysis, investigation, methodology, project administration, software, validation, visualization, writing}
%	 (original draft)}% \& review/editing)}

\item J.F. Crenshaw, J.B. Kalmbach, {\bf A.I. Malz}, A.J. Connolly. 2021. American Astronomical Society, AAS Meeting \#238, id. 230.01. ``\texttt{PZFlow}: normalizing flows for cosmology, with applications to forward modeling galaxy photometry" \deemph{(contributed poster)}
%	\descr{Contributor: supervision, validation}

\item {\bf A.I. Malz}. 2021. American Astronomical Society, AAS Meeting \#237, LSST-DESC Special Session, id. 443.05. ``The DESC Photometric Redshifts Working Group: Challenges \& Opportunities'' \deemph{(contributed talk)}
%	\descr{{\bf Sole author}}

\item {\bf A.I. Malz}. 2019. American Astronomical Society, AAS Meeting \#233, Surveys \& Large Programs, id. 313.05D. ``Probabilistic data analysis methods for large photometric surveys'' \deemph{(contributed talk)}
%	\descr{{\bf Sole author}}
%
\item {\bf A.I. Malz}. 2019. American Astronomical Society, AAS Meeting \#233, Larger Efforts in Education \& Public Outreach, id. 212.05. ``The Photometric LSST Astronomical Time Series Classification Challenge (PLAsTiCC): challenge design and evaluation criteria” \deemph{(contributed talk)}
%	\descr{{\bf Sole author}}

\item C.M. Peters, {\bf A.I. Malz} \& R. Hlozek. 2018. American Astronomical Society, AAS Meeting \#231, id. 245.03. ``Supernova Cosmology Inference with Probabilistic Photometric Redshifts'' \deemph{(contributed poster)}
%	\descr{{\bf Lead author}: conceptualization, data curation, formal analysis, investigation, methodology, software, validation, visualization, writing}
%	 (original draft)}% \& review/editing)}

\item {\bf A.I. Malz} \& S. Shandera. 2014. American Astronomical Society, AAS Meeting \#223, id. 456.04. ``Probing Gravity in the High-Redshift Universe with HETDEX'' \deemph{(contributed poster)}
%	\descr{{\bf Lead author}; conceptualization, data curation, formal analysis, investigation, methodology, visualization, writing}
%	 (original draft)}% \& review/editing)}

\item {\bf A.I. Malz}, R. Rich \& S. Lepine. 2009. American Astronomical Society, AAS Meeting \#213, id. 602.04. ``Low-mass Binaries in the Galactic Halo Resolved by Adaptive Optics'' \deemph{(contributed poster)}
%	\descr{{\bf Lead author}; formal analysis, funding acquisition, investigation, writing}
%	 (original draft)}% \& review/editing)}
\end{list}
